### 2014-12-08 Draft/abstract.tex
updated based on Dr. Xie's Comments

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing program analysis tools that require formal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language text in API documents.}
Since, API documents are often verbose, manually writing formal temporal constraints can be prohibitively time consuming and error prone.
To address this issue,
we propose \tool, a Machine Learning (ML) and Natural Language Processing (NLP) based
approach for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 77.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, \tool\ also achieves an accuracy of 70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most API do not have formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from \amazonAPI, \paypalAPI\ and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrate that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

### 2014-12-08 Draft/approach.tex
updated based on Dr. Xie's Comments

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
\tool\ consists of following major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
We next describe each component in detail.

@@

The preprocessor accepts the API documents and extracts method descriptions from it.
In particular, the preprocessor extracts the following fields from the method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown (or errors returned) by the methods}.

This step is required to extract the desired descriptive text from the API documents.
Different API documents may have different styles of presenting information to developers.
This difference in style may also include the difference in the level of detail presented to developers.
\tool\ thus relies on only basic fields that are generally available for API methods across different presentation styles.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
%From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
%However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, each sentence is annotated with: \textit{1)POS tags, 2)named-entity annotations, and 3)Stanford-typed dependencies.}
For more details on these techniques and their application, please refer to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

Next we use an example to illustrate the annotations added by the NLP Parser. Consider the sentence from the example section \textbf{\textit{`All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''}}. Figure~\ref{fig:standep} shows the sentence annotated by NLP parser. Each word (occurs first) is followed by the Part-Of-Speech (POS) tag of the word (in green), which is further followed by the name of Stanford dependency connecting the actual word of the sentence to its predecessor.
%For more details on Stanford-typed dependencies and POS tags, please refer to ~\cite{Marneffe06LREC,Marneffe08COLING}.

@@

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences. Since \tool\ seeks to achieve a binary classification of the API sentences, we chose to train our model using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods  and is shown to be comparative other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}. The model can be trained offline or else by the users of the approach if better accuracy is required for specific data.

Feature selection is an important factor for the accuracy any classification method. Particularly, for na{\"i}ve Bayes classifier which assumes each feature independently contributes towards the final probability of classification. In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features. We next describe the features we chose for training our model along with the rationale for selecting such features.

@@

	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary or exception/error summary as captured by pre-processor phase. The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.

	\item \textbf{Lemmatization}: The feature is the base form of a word. In linguistic lemmatization is the reduction of operational form of a word to its base form. For instance ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke. The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word as an independent feature.

	\item \textbf{Stopword Reduction}: In linguistics stop words are the frequently occurring words that can easily be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc... The rationale for filtering the stop words is to reduce the size of feature set that otherwise considers such word as an independent feature but are often noise. Stop word list is further augmented by adding to them the words that occur exactly once in the training corpus to avoid over-fitting of the model to the training corpus.

	\item \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics. In particular we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''. For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies. These are both added to the feature set.

@@

The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. We thus break down the sentence into two smaller tractable sentences:

@@

Table~\ref{tab:semanticTemplates} shows a list the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by our shallow parser when the template is applicable.
All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\textbf{Stanford-typed Dependencies}: This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

@@

A key way of identifying reference to a method in the API by \tool\ is the employment of a semantic graph of an API.
We propose to initially infer such graphs from API documents.
Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed previously by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.

>>>>

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of \tool\ approach.
\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
Additionally, there is an optional model trainer component and external NLP parser component.
We next describe each component in detail.

@@

The preprocessor accepts the API documents and extracts method descriptions.
In particular, the preprocessor extracts the following fields from the method descriptions: 
1) \textit{Summary of the API method},
2) \textit{Summary and type information of parameters of the API method}, 
3) \textit{Summary and type information of return values of the method}, and
4) \textit{Summary and type information of exceptions thrown (or errors returned) by the methods}.

This step is required to extract the desired descriptive text from the API documents.
Different API documents may have different styles of presenting information to developers.
This difference in style may also include the difference in the level of the details presented to developers.
\tool\ relies only on basic fields that are generally available for API methods across different presentation styles.

@@

The NLP parser accepts the pre-processed documents and annotates every sentence in each document using core NLP techniques described in Section~\ref{sub:CoreNLPback}.
%From an implementation perspective, we chose the Stanford parser~\cite{Manning:01}.
%However, this component can be implemented using any other existing NLP libraries or approaches.
In particular, each sentence is annotated with: \textit{1) POS tags, 2) named-entity annotations, and 3) Stanford-typed dependencies.}
For more details on these techniques and their application, please to ~\cite{Marneffe06LREC, Marneffe08COLING, pandita12:inferring, pandita13:WHYPER, thummalapentaICSE12}.

@@

Next we use an example to illustrate the annotations added by the NLP Parser. Consider the sentence from the example section \textbf{\textit{`All objects (including all object versions and Delete Markers) in the bucket must be deleted before the bucket itself can be deleted.''}}. Figure~\ref{fig:standep} shows the sentence annotated by NLP parser. Each word (occurs first) is followed by the Part-Of-Speech (POS) tag of the word (in green), which is further followed by the name of Stanford dependency connecting the actual word of the sentence to its predecessor.
From an implementation perspective, this component can be implemented using any existing NLP libraries or approaches such as Stanford Parser~\cite{SNLP1}.

@@

The goal of model construction is to use a small set of manually classified temporal constraint sentences of a representative API to construct a model to automatically classify the unlabeled sentences. 
From an implementation perspective, we can use any of the standard off-the-shelf classifiers to train the model, since \tool\ seeks to achieve only a binary classification of the API sentences.
For instance, model can be trained using na{\"i}ve Bayes classifier which is the simplest probabilistic classification methods and is shown to be comparative to other advanced classification methods given appropriate prepossessing~\cite{rennie2003tackling}.
The model can be trained offline or else by the users of the approach if better accuracy is desired for domain-specific data.

Feature selection is an important factor for the accuracy any classification method.
%For instance, na{\"i}ve Bayes classifier assumes each feature independently contributes towards the final probability of classification.
In the simplest form, each word occurring in a sentence is considered as a feature. However, such an approach may lead to overly specific models, and therefore \tool\ approach employs preprocessing for generic features. We next describe the features we chose for training our model along with the rationale for selecting such features.

@@

	\item \textbf{Sentence Type}: The context of sentence, whether the sentence appears as method summary, parameter summary, return value summary, or exception/error summary as captured by pre-processor phase. The rationale is that a majority of the temporal constraint sentences are either summary or exception sentences.

	\item \textbf{Lemmatization}: The feature is the base form of a word. In linguistic, lemmatization is the reduction of operational form of a word to its base form. For instance, ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke. The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word as an independent feature.

	\item \textbf{Stopword Reduction}: In linguistics, stopwords are the frequently occurring words that can be ignored and are often considered noise, such as ``the'' , ``of'', ``to'' etc... The rationale for filtering the stopwords is to reduce the size of feature set that otherwise considers such words (despite being noise) as an independent features. Stopword list is further augmented by adding to them the words that occur exactly once in the training corpus to avoid over-fitting of the model to the training corpus.

	\item \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics. In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''. For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies. These are both added to the feature set.

@@

The Stanford parser finds it difficult to annotate accurately the Stanford-typed dependencies of the sentence because of presence of different clauses acting on different subject-object pairs.
As shown in figure~\ref{fig:standep} the word including is annotated with Stanford-typed dependencies ``dep'' that is a catch all dependency. A catch all dependency is selected by a parser when no other appropriate dependency can be selected. We thus break down the sentence into two smaller tractable sentences:

@@

Table~\ref{tab:semanticTemplates} lists the semantic templates used in this phase.
Column ``Template'' describes conditions where the template is applicable and Column ``Summary'' describes the action taken by \tool\ when the template is applicable.
%All of these semantic templates are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}.
With respect to the previous example the template 3 \textit{( A noun phrase followed by another noun/pronoun/verb phrase in brackets)} is applicable.
Thus our shallow parser breaks the sentence into two individual sentences.

@@

\textbf{Stanford-typed Dependencies}: After complex sentences (whenever applicable) have been broken to simple sentnces, this phase generates an intermediate (FOL) representation of the sentences. This phase is equivalent to the intermediate-representation technique described in Section~\ref{sub:SENLPback}. Figure~\ref{fig:FOLTree} is the FOL representation of the sentence  \textit{``All objects in the bucket must be deleted before the bucket itself can be deleted''}. All the leaf nodes (entities) are represented as the bold words. For readability each node is appended with a number representing the in-order traversal index of the tree.

@@

A key way of identifying reference to a method in the API by \tool\ is the employment of a semantic graph of an API.
We propose to initially infer such graphs from API documents.
Ad hoc creation of semantic graph is prohibitively time consuming and may be error prone.
We thus employ a systematic methodology (proposed by Pandita et al. ~\cite{pandita13:WHYPER}) to infer semantic graphs from API documents.

### 2014-12-08 Draft/background.tex
updated based on Dr. Xie's Comments

%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are used in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state of the art approaches have demonstrated to be effective in classifying POS tags for well written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking thus further enhances the syntax of a sentence on top of POS tagging. Current state-of-the-art approaches can effectively classify phrases and clauses over well written news articles.

@@

We next present Software Engineering (SE) specific NLP techniques.

@@

Consider the word \CodeIn{POST} for instance. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

Noun Boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus in turn increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a group of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in previous work to achieve the desired reduction of lexical tokens:

@@

\item \textbf{Period Handling}. Besides marking the end of a sentence in simplistic English, the character period (`.') has other legal usages as well such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

@@

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations mixed with text.
This phenomenon can result in subsequent components to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
In particular, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator based on shallow parsing~\cite{Branimir2000} techniques. 
The shallow parser itself is implemented as a sequence of cascading finite state machines based on the function of Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

>>>>

%In particular, this work proposes novel techniques on top of previously proposed techniques~\cite{pandita12:inferring, pandita13:WHYPER} to demonstrate the effectiveness of applying NLP on API documents.
We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.

@@

\textbf{Parts Of Speech (POS) tagging}~\cite{Klein03,KleinNIPS03}. Also known as \textit{`word tagging'}, \textit{`grammatical tagging'} and \textit{`word-sense disambiguation'}, these techniques aim to identify the part of speech (such as noun, verbs, etc.), a particular word in a sentence belongs to. The most commonly used technique is to train a classification parser over a previously known data set. Current state-of-the-art approaches have demonstrated to be effective in classifying POS tags for well-written news articles.

\textbf{Phrase and Clause Parsing}. Also known as chunking, this technique divides a sentence into a constituent set of words (or phrases) that logically belong together (such as a Noun Phrase and Verb Phrase). Chunking further enhances the syntax of a sentence in addition to POS tagging. Current state-of-the-art approaches can effectively classify phrases and clauses over well-written news articles.

@@

We next present SE specific NLP techniques.

@@

For instance, consider the word \CodeIn{POST}. 
The online Oxford dictionary\footnote{\url{http://oxforddictionaries.com/us/definition/american_english/post?q=POST}} has eight different definition of word \CodeIn{POST}, and none of them describes \CodeIn{POST} as an HTTP method\footnote{In HTTP vocabulary \CodeIn{POST} means: \textit{``Creates a new entry in the collection.
The new entry's URI is assigned automatically and is usually returned by the operation''}}
supported by REST API.
Thus existing POS tagging techniques fail to accurately annotate the POS tags of the sentences involving word \CodeIn{POST}.

Noun boosting identifies such words from the sentences based on a domain-specific dictionaries, and annotates them appropriately.
The annotation assists the POS tagger to accurately annotate the POS tags of the words thus increasing accuracy of advanced NLP techniques such as chunking and typed dependency annotation.

\textbf{Lexical Token Reduction}~\cite{pandita13:WHYPER}.
These are a collection of generic preprocessing heuristics to further improve the accuracy of core NLP techniques.
The accuracy of core NLP techniques is often inversely proportional to the number of lexical tokens in a sentence.
Thus, the reduction in the number of lexical tokens greatly increases the accuracy of core NLP techniques. 
In particular, following heuristics have been used in related work~\cite{pandita12:inferring,pandita13:WHYPER} to achieve the desired reduction of lexical tokens:

@@

\item \textbf{Period Handling}. Besides marking the end of a sentence in generic English, the character period (`.') has other legal usages as well, such as decimal representation (periods between numbers).
Although legal, such usage hinder detection of sentence boundaries, thus causing core NLP techniques to return incorrect or imprecise results.
The text is pre-processed by annotating these usages for accurate detection of sentence boundaries.

@@

\item \textbf{Abbreviation Handling}. Natural-language sentences often consist of abbreviations interleaved with text.
This interleaving may result in POS tagger to incorrectly parse a sentence.
This heuristic finds such instances and annotates them as a single lexical unit.
For example, text followed by abbreviations such as \textit{``Access Control Lists (ACL)''} is treated as single lexical unit.
Detecting such abbreviations is achieved by using the common structure of abbreviations and encoding such structures into regular expressions.
Typically, regular expressions provide a reasonable approximation for handling abbreviations.

@@

\textbf{Intermediate-Representation Generation}~\cite{pandita13:WHYPER}.
This technique accepts the syntax-annotated sentences (grammatical and semantic) and builds a First-Order-Logic (FOL) representation of the sentence.
Earlier researches have shown the adequacy using FOL for NLP related analysis tasks~\cite{Sinha2009,Sinha2010,pandita12:inferring}.
Particularly, WHYPER~\cite{pandita13:WHYPER} demonstrates the effectiveness of this technique, by constructing an intermediate representation generator from semantically annotated sentences. 
The component is implemented as a sequence of cascading finite state machines based on the function of annotated Stanford-typed dependencies~\cite{Marneffe06LREC,Marneffe08COLING,Klein03,KleinNIPS03}.

### 2014-12-08 Draft/conclusion.tex
updated based on Dr. Xie's Comments

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 77\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 63 formal temporal constraints from these sentences.

>>>>

Despite being highly desirable, most APIs are not equipped with formal temporal constraints.
In contrast, documentation of API methods contains detailed specifications of temporal constraints in natural language text.
Manually writing formal specifications based on natural language text in API documents is prohibitively time consuming and error prone.
To address this issue, we have proposed a novel approach called \tool\ to infer temporal constraints from natural language text of API documents.
We applied \tool\ to infer temporal constraints from
\paypalAPI, \amazonAPI, and  
commonly used package \CodeIn{java.io} in the JDK API.
Our evaluation results show that \tool\ effectively identifies sentences describing
temporal constraints with an average 79\% precision and 60\% recall,
from more than 4000 sentences in subject API documents.
Furthermore, \tool\ also achieved an accuracy of
70\% in inferring 77 formal temporal constraints from these sentences.
